FraCaS: 80 percent complete

### 2019-01-18 paper2018/paper.tex
overruled cases

We classify as YES if a proof can be constructed from the premises to
the hypothesis, NO if a proof of the negated hypothesis can be
constructed and UNK otherwise.\footnote{Because we work with a non-decidable logic, that poses a theoretical question that we address below.}

@@

\todo{rejected and changed cases in FraCaS}
\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & \# examples & Ours     & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74) & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82      & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20) & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87      & .56    & .48  & .45  &  -       \\
8 & Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92      & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 262         & .89      & .83    & .69  & .50  & .85  \\
  &              &             & (259)    & (174)  & (174)& (174)& (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of examples shown in the
    third column, the actual number of examples attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}.  }
\end{table}

>>>>

FraCaS intends to classify each problem as either entailment (YES),
entailment of the opposite (NO) or no entailment (UNK).  For this
work, we have amended FraCaS to address a few problems. First, certain
test case are not formed correctly. Those were identified by Bill
MacCartney as ``undef'', and we removed those. Second, a few test
cases occurs twice in the suite, but with two different answers (one
YES and one UNK), with the annotation that those correspond to
different readings. However, elsewhere in the suite, if a problem has
several readings but only one has entailment, it occurs only once and
is marked as YES. To make the test suite consistent, if one reading
yields entailment we have always considered it as YES. Finally, we
have removed case 199 (which appears to be vacuous), and changed the
following cases, which appeared to have been misclassified. We note
that the majority of the mistaken classifications occur in sections 3
and 4, which have not been previously attempted and thus, we propose,
have not been properly scrutinized.

\begin{center}
\begin{tabular}{ccc}
 test case & new class & comment \\ \hline
    005 & UNK & missing hypothesis: there are italian tenors \\
   056 &  Yes & Already identified as such by MacCartney \\
  069 & Unk & Mary could have used someone else's workstation \\
  119 & Unk & \textit{ibid.} \\
  181 & Yes & for the same reason as 180 \\
  226 & Yes &
\end{tabular}
\end{center}

Our system classifies a case as YES if a proof can be constructed from
the premises to the hypothesis, NO if a proof of the negated
hypothesis can be constructed and UNK otherwise. Because we work with
a non-decidable logic, one can not \emph{in general} conclude
decisively that no proof exists. Thus, we consider here that no proof
exists if it cannot be constructed with reasonable effort. In
particular, we test at the minimum that the automatic proof search
built in Coq does not succeed before classifying a problem as UNK.

@@

\providecommand\forcecenter{\multicolumn{1}{c}}
\begin{table}
  \centering
\begin{tabular}{rlrrrrrr}
  & Section      & \# examples & Ours     & FraCoq & MINE & Nut  & Langpro  \\ \hline
1 & Quantifiers  & 75          & .96 (74) & .96    & .77  & .53  & .93 (44) \\
2 & Plurals      & 33          & .82      & .76    & .67  & .52  & .73 (24) \\
3 & Anaphora     & 28          & .86      &   -    & -    & -    &  -       \\
4 & Ellipsis     & 52          & .87      &   -    & -    & -    &  -       \\
5 & Adjectives   & 22          & .95 (20) & .95    & .68  & .32  & .73 (12) \\
6 & Comparatives & 31          & .87      & .56    & .48  & .45  &  -       \\
8 & Verbs        & 8           & .75      &   -    & -    & -    &  -       \\
9 & Attitudes    & 13          & .92      & .85    & .77  & .46  & .92 (9)  \\ \hline
  & Total        & 262         & .89      & .83    & .69  & .50  & .85  \\
  &              &             & (259)    & (174)  & (174)& (174)& (89)
  \end{tabular}
  \caption{Overview of the accuracy of our system compared to others.
    ``Ours" refers to the approach presented in this paper. When a
    system does not handle the nominal number of examples shown in the
    third column, the actual number of examples attempted is shown in
    parentheses.  ``FraCoq'' refers to the work of
    \citet{bernardy_type_2017}. ``MINE" refers to the approach of
    \citet{Mineshima:2015}, ``NUT" to the CCG system that utilizes the
    first-order automated theorem prover \textit{nutcracker} described
    by \citet{bos:2008}, and ``Langpro" to the system presented by
    \citet{Abzianidze:2015}.  }
\end{table}
